\documentclass[10pt]{report}
\begin{document}
\title{
 {REPORT ON HOW TO COOK CHICKEN WITHOUT OIL}\\
{\large  COLLEGE OF COMPUTING AND INFORMATION SCIENCES}\\
{\large BACHELOR OF SCIENCE IN COMPUTER SCIENCE}
{TABLE OF CONTENTS}\\
{\large Abstraction.......................2}\\
{\large Introduction.......................2}\\
{\large Methodology.......................2}\\
{\large Results..............................2}\\
{\large Conclusion..........................2}\\
{\large Recommendation..................2}}

\author {
{\large KABUUNGA HAMIDU}
{15/U/5389/PS}}





\maketitle
\section{HOW TO COOK CHICKEN WIHOUT OIL}

\subsection{Abstract}
	{The aim of this report was to investigate how to fry chicken without oil. The results indicate that this is very rare in many homes since most of them always prefer chicken fried with oil. I basically used sampling by trying it out myself and I came up with a conclusion that cooking chicken without oil is an ideal option I would like to explore. I strongly recommended it because its not only delicious but also healthy.}
\subsection{Introduction}
{Many people enjoy meals due to very many factors like culture, appetite, money etc. When it comes to chicken, its one of some people’s favorites. Many people often eat chicken fried with oil which is not bad but also trying out the one without oil is an experience I explored and one to remember. 
The purpose of this research was to get to know how to discover new ways on how people can enjoy meals like chicken without necessarily using oil.}
\subsection{Methodology}
{I carried out the research myself by organizing all what I needed to cook this chicken having in mind I shouldn’t use cooking oil. I first went to buy the hen its self, slaughtered it and cleaned it as possible.
After all this, I bought all the ingredients required like tomatoes, onions, carrots, garlic and many others. I first cut it into pieces and placed them in an empty saucepan already on fire. I allowed it to cook on its own for close to 20 minutes after which I put all the ingredients mixed up and added some little water. For about 30 more minutes the chicken was ready for dinner.}
\subsection{Results}
{The results from this were very positive as everyone who tasted it was overwhelmingly wondering how it would have been possible not to use oil to come out with such a great meal. The captured results showed that 9 people out of the 10 who consumed the chicken enjoyed the meal to their satisfaction.

\subsection{Conclusion}
{From all people who tasted the meal, I concluded that cooking chicken without oil is an ideal option to explore, better for our health as well as enjoyment.}
\subsection{Recommendations}
{I can only recommend people to try out this adventure but all u need is to have a lot more ingredients for the best meal .}


\end{document}